### 2017-10-18 Sections/authors.tex
Amended author list

@@

\author{Peter P. Rohde}
\email[To whom correspondence should be addressed: ]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007, Australia}
\affiliation{Hearne Institute for Theoretical Physics and Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, LA 70803, United States}

>>>>

\author{(in no particular order)\\[2mm]}

@@

\author{Peter P. Rohde}
\email[To whom correspondence should be addressed: ]{dr.rohde@gmail.com}
\homepage{http://www.peterrohde.org}
\affiliation{Centre for Quantum Software \& Information (QSI), Faculty of Engineering \& Information Technology, University of Technology Sydney, NSW 2007\\Australia}
\affiliation{Hearne Institute for Theoretical Physics and Department of Physics \& Astronomy, Louisiana State University, Baton Rouge, LA 70803, United States}

%
% Samuel Marks
%

\author{Samuel Marks}
\affiliation{Sydney Medical School, Faculty of Medicine, University of Sydney, NSW 2006, Australia}
\affiliation{Glaucoma Cell Biology Group, Westmead Institute for Medical Research, 176 Hawkesbury Rd, Westmead NSW 2145\\Australia}
